---
title: "Distance to perimeter"
author: "Anna Talucci"
date: '2022-10-18'
output: html_document
---

# Overview

Distance from field site to perimeter.

-- To measure the distance to the perimeter polygons need to be converted to line strings
-- Measure done in equal area projection, sphere and ellipsoid


**Process by fire event**
# Packages

```{r}
library(tidyverse)
library(sp)
library(sf)
library(ids)
library(units)
library(geosphere)
```

# Projections
```{r}
wgs_proj = "+proj=longlat +datum=WGS84 +no_defs"
```

```{r}
ea_proj = "+proj=aea +lat_0=50 +lon_0=-154 +lat_1=55 +lat_2=65 +x_0=0 +y_0=0 +datum=NAD83 +units=m +no_defs"
```


# Field points by Year
## Data

### 2015
```{r}
fieldAggie2015=st_read("../data/FieldPointsShp/FieldAggie2015.shp", "FieldAggie2015")
fieldBaker2015=st_read("../data/FieldPointsShp/FieldBaker2015.shp", "FieldBaker2015")
fieldHay2015=st_read("../data/FieldPointsShp/FieldHay2015.shp", "FieldHay2015")
fieldUscreek2015=st_read("../data/FieldPointsShp/FieldUSCreek2015.shp", "FieldUSCreek2015")
```
### 2019
```{r}
fieldBear2019=st_read("../data/FieldPointsShp/FieldBear2019.shp", "FieldBear2019")
fieldCripple2019=st_read("../data/FieldPointsShp/FieldCripple2019.shp", "FieldCripple2019")
fieldFrozen2019=st_read("../data/FieldPointsShp/FieldFrozen2019.shp", "FieldFrozen2019")
fieldHess2019=st_read("../data/FieldPointsShp/FieldHess2019.shp", "FieldHess2019")
fieldMarr2019=st_read("../data/FieldPointsShp/FieldMarr2019.shp", "FieldMarr2019")
fieldPreach2019=st_read("../data/FieldPointsShp/FieldPreach2019.shp", "FieldPreach2019")
fieldShovel2019=st_read("../data/FieldPointsShp/FieldShovel2019.shp", "FieldShovel2019")
fieldTractor2019=st_read("../data/FieldPointsShp/FieldTractor2019.shp", "FieldTractor2019")
fieldBC0052019=st_read("../data/FieldPointsShp/FieldBC0052019.shp", "FieldBC0052019")
fieldMA0142019 = st_read("../data/FieldPointsShp/FieldMA0142019.shp", "FieldMA0142019")
```

```{r}
fieldpts2020 = st_read("../data/FieldPointsShp/FieldPoints2020.shp", "FieldPoints2020")
fieldpts2021 = st_read("../data/FieldPointsShp/FieldPoints2021.shp", "FieldPoints2021")
```

# Process by fire event
# 2015
## 2015 Aggie
### Data
```{r}
aggie2015 = st_read("../data/PerimeterPoints/AggiePtsLatLon2015.shp", "AggiePtsLatLon2015")
```

### 2D Find nearest point and measure distance
```{r}
edgeAggie2015=fieldAggie2015 %>%
  mutate(nearestEdge = st_nearest_feature(., aggie2015)) %>%
  mutate(edgeEa = st_distance(., aggie2015[nearestEdge,], by_element=TRUE, which = "Euclidean")) %>%
  st_drop_geometry(.)

```


### 3D
#### join nearest feature
 Join df with df1, based on the nearest feature:
```{r}
Aggie_near2015 <- st_join(fieldAggie2015, aggie2015, join = st_nearest_feature) %>%
  st_drop_geometry(.) %>%
  dplyr::select(-offcl__.y, -FireYr.y) %>%
  rename(FireYr = FireYr.x, offcl__ = offcl__.x)
```

```{r}
Aggie_near2015
```
```{r}
edgeSphAggie2015 = Aggie_near2015 %>% 
  rowwise() %>% 
  mutate(distSph = distHaversine(c(longitd, latitud), c(LON, LAT)))
  
```

```{r}
edgeEllpAggie2015 = Aggie_near2015 %>% 
  rowwise() %>% 
  mutate(distEllp = distVincentyEllipsoid(c(longitd, latitud), c(LON, LAT), a=6378137, b=6356752.3142, f=1/298.257223563))
```

```{r}
head(edgeAggie2015)
head(edgeSphAggie2015)
head(edgeEllpAggie2015)
```

#### Combine into single DF
```{r}

edgeAggie2015 %>%
  full_join(edgeSphAggie2015, by = c("project", "FireYr", "fir_scr", "offcl__", "site", "plot", "latitud", "longitd", "elevatn", "slope", "aspect", "mstr_cl" ))

```
```{r}
joinAggie2015_1 = edgeAggie2015 %>%
  full_join(edgeSphAggie2015, by = c("project", "FireYr", "fir_scr", "offcl__", "site", "plot", "latitud", "longitd", "elevatn", "slope", "aspect", "mstr_cl" )) %>%
  full_join(edgeEllpAggie2015, by = c("project", "FireYr", "fir_scr", "offcl__", "site", "plot", "latitud", "longitd", "elevatn", "slope", "aspect", "mstr_cl", "LAT", "LON" )) %>%
  drop_units()

joinAggie2015_1
```



## Baker
### Data
```{r}
Baker2015 = st_read("../data/PerimeterPoints/BakerPtsLatLon2015.shp", "BakerPtsLatLon2015")
```
### 2D Find nearest point and measure distance
```{r}
edgeBaker2015=fieldBaker2015 %>%
  mutate(nearestEdge = st_nearest_feature(., Baker2015)) %>%
  mutate(edgeEa = st_distance(., Baker2015[nearestEdge,], by_element=TRUE, which = "Euclidean")) %>%
  st_drop_geometry(.)

```


### 3D
#### join nearest feature
 Join df with df1, based on the nearest feature:
```{r}
Baker_near2015 <- st_join(fieldBaker2015, Baker2015, join = st_nearest_feature) %>%
  st_drop_geometry(.) %>%
  dplyr::select(-offcl__.y, -FireYr.y) %>%
  rename(FireYr = FireYr.x, offcl__ = offcl__.x)
```

```{r}
Baker_near2015
```
```{r}
edgeSphBaker2015 = Baker_near2015 %>% 
  rowwise() %>% 
  mutate(distSph = distHaversine(c(longitd, latitud), c(LON, LAT)))
  
```

```{r}
edgeEllpBaker2015 = Baker_near2015 %>% 
  rowwise() %>% 
  mutate(distEllp = distVincentyEllipsoid(c(longitd, latitud), c(LON, LAT), a=6378137, b=6356752.3142, f=1/298.257223563))
```

```{r}
edgeBaker2015
edgeSphBaker2015
edgeEllpBaker2015
```

#### Combine into single DF
```{r}
joinBaker2015_1 = edgeBaker2015 %>%
  full_join(edgeSphBaker2015, by = c("project", "FireYr", "fir_scr", "offcl__", "site", "plot", "latitud", "longitd", "elevatn", "slope", "aspect", "mstr_cl" )) %>%
  full_join(edgeEllpBaker2015, by = c("project", "FireYr", "fir_scr", "offcl__", "site", "plot", "latitud", "longitd", "elevatn", "slope", "aspect", "mstr_cl", "LAT", "LON" )) %>%
  drop_units()

joinBaker2015_1
```

## 2015 Hay
### Data
```{r}
Hay2015 = st_read("../data/PerimeterPoints/HayPtsLatLon2015.shp", "HayPtsLatLon2015")
```

### 2D Find nearest point and measure distance
```{r}
edgeHay2015=fieldHay2015 %>%
  mutate(nearestEdge = st_nearest_feature(., Hay2015)) %>%
  mutate(edgeEa = st_distance(., Hay2015[nearestEdge,], by_element=TRUE, which = "Euclidean")) %>%
  st_drop_geometry(.)

```


### 3D
#### join nearest feature
 Join df with df1, based on the nearest feature:
```{r}
Hay_near2015 <- st_join(fieldHay2015, Hay2015, join = st_nearest_feature) %>%
  st_drop_geometry(.) %>%
  dplyr::select(-offcl__.y, -FireYr.y) %>%
  rename(FireYr = FireYr.x, offcl__ = offcl__.x)
```

```{r}
Hay_near2015
```
```{r}
edgeSphHay2015 = Hay_near2015 %>% 
  rowwise() %>% 
  mutate(distSph = distHaversine(c(longitd, latitud), c(LON, LAT)))
  
```

```{r}
edgeEllpHay2015 = Hay_near2015 %>% 
  rowwise() %>% 
  mutate(distEllp = distVincentyEllipsoid(c(longitd, latitud), c(LON, LAT), a=6378137, b=6356752.3142, f=1/298.257223563))
```

```{r}
edgeHay2015
edgeSphHay2015
edgeEllpHay2015
```

#### Combine into single DF
```{r}
joinHay2015_1 = edgeHay2015 %>%
  full_join(edgeSphHay2015, by = c("project", "FireYr", "fir_scr", "offcl__", "site", "plot", "latitud", "longitd", "elevatn", "slope", "aspect", "mstr_cl" )) %>%
  full_join(edgeEllpHay2015, by = c("project", "FireYr", "fir_scr", "offcl__", "site", "plot", "latitud", "longitd", "elevatn", "slope", "aspect", "mstr_cl", "LAT", "LON" )) %>%
  drop_units()

joinHay2015_1
```

## 2015 US Creek
### Data
```{r}
Uscreek2015 = st_read("../data/PerimeterPoints/USCreekPtsLatLon2015.shp", "USCreekPtsLatLon2015")
```


### 2D Find nearest point and measure distance
```{r}
edgeUscreek2015=fieldUscreek2015 %>%
  mutate(nearestEdge = st_nearest_feature(., Uscreek2015)) %>%
  mutate(edgeEa = st_distance(., Uscreek2015[nearestEdge,], by_element=TRUE, which = "Euclidean")) %>%
  st_drop_geometry(.)

```


### 3D
#### join nearest feature
 Join df with df1, based on the nearest feature:
```{r}
Uscreek_near2015 <- st_join(fieldUscreek2015, Uscreek2015, join = st_nearest_feature) %>%
  st_drop_geometry(.) %>%
  dplyr::select(-offcl__.y, -FireYr.y) %>%
  rename(FireYr = FireYr.x, offcl__ = offcl__.x)
```

```{r}
Uscreek_near2015
```
```{r}
edgeSphUscreek2015 = Uscreek_near2015 %>% 
  rowwise() %>% 
  mutate(distSph = distHaversine(c(longitd, latitud), c(LON, LAT)))
  
```

```{r}
edgeEllpUscreek2015 = Uscreek_near2015 %>% 
  rowwise() %>% 
  mutate(distEllp = distVincentyEllipsoid(c(longitd, latitud), c(LON, LAT), a=6378137, b=6356752.3142, f=1/298.257223563))
```

```{r}
edgeUscreek2015
edgeSphUscreek2015
edgeEllpUscreek2015
```

#### Combine into single DF
```{r}
joinUscreek2015_1 = edgeUscreek2015 %>%
  full_join(edgeSphUscreek2015, by = c("project", "FireYr", "fir_scr", "offcl__", "site", "plot", "latitud", "longitd", "elevatn", "slope", "aspect", "mstr_cl" )) %>%
  full_join(edgeEllpUscreek2015, by = c("project", "FireYr", "fir_scr", "offcl__", "site", "plot", "latitud", "longitd", "elevatn", "slope", "aspect", "mstr_cl", "LAT", "LON" )) %>%
  drop_units()

joinUscreek2015_1
```

## Combine 2015
```{r}
combo2015_1 = rbind(joinAggie2015_1, joinBaker2015_1)
combo2015_2 = rbind(joinHay2015_1, joinUscreek2015_1)
combo2015All = rbind(combo2015_1, combo2015_2)
```

```{r}
combo2015All
```

# 2019
## 2019 Bear 
### Data

```{r}
Bear2019 = st_read("../data/PerimeterPoints/BearPtsLatLon2019.shp", "BearPtsLatLon2019")
```

### 2D Find nearest point and measure distance
```{r}
edgeBear2019=fieldBear2019 %>%
  mutate(nearestEdge = st_nearest_feature(., Bear2019)) %>%
  mutate(edgeEa = st_distance(., Bear2019[nearestEdge,], by_element=TRUE, which = "Euclidean")) %>%
  st_drop_geometry(.)

```


### 3D
#### join nearest feature
 Join df with df1, based on the nearest feature:
```{r}
Bear_near2019 <- st_join(fieldBear2019, Bear2019, join = st_nearest_feature) %>%
  st_drop_geometry(.) %>%
  dplyr::select(-offcl__.y, -FireYr.y) %>%
  rename(FireYr = FireYr.x, offcl__ = offcl__.x)
```

```{r}
Bear_near2019
```
```{r}
edgeSphBear2019 = Bear_near2019 %>% 
  rowwise() %>% 
  mutate(distSph = distHaversine(c(longitd, latitud), c(LON, LAT)))
  
```

```{r}
edgeEllpBear2019 = Bear_near2019 %>% 
  rowwise() %>% 
  mutate(distEllp = distVincentyEllipsoid(c(longitd, latitud), c(LON, LAT), a=6378137, b=6356752.3142, f=1/298.257223563))
```

```{r}
edgeBear2019
edgeSphBear2019
edgeEllpBear2019
```

#### Combine into single DF
```{r}
joinBear2019_1 = edgeBear2019 %>%
  full_join(edgeSphBear2019, by = c("project", "FireYr", "fir_scr", "offcl__", "site", "plot", "latitud", "longitd", "elevatn", "slope", "aspect", "mstr_cl" )) %>%
  full_join(edgeEllpBear2019, by = c("project", "FireYr", "fir_scr", "offcl__", "site", "plot", "latitud", "longitd", "elevatn", "slope", "aspect", "mstr_cl", "LAT", "LON" )) %>%
  drop_units()

joinBear2019_1
```


## 2019 Cripple
### Data
```{r}
Cripple2019 = st_read("../data/PerimeterPoints/CripplePtsLatLon2019.shp", "CripplePtsLatLon2019")
```

### 2D Find nearest point and measure distance
```{r}
edgeCripple2019=fieldCripple2019 %>%
  mutate(nearestEdge = st_nearest_feature(., Cripple2019)) %>%
  mutate(edgeEa = st_distance(., Cripple2019[nearestEdge,], by_element=TRUE, which = "Euclidean")) %>%
  st_drop_geometry(.)

```


### 3D
#### join nearest feature
 Join df with df1, based on the nearest feature:
```{r}
Cripple_near2019 <- st_join(fieldCripple2019, Cripple2019, join = st_nearest_feature) %>%
  st_drop_geometry(.) %>%
  dplyr::select(-offcl__.y, -FireYr.y) %>%
  rename(FireYr = FireYr.x, offcl__ = offcl__.x)
```

```{r}
Cripple_near2019
```
```{r}
edgeSphCripple2019 = Cripple_near2019 %>% 
  rowwise() %>% 
  mutate(distSph = distHaversine(c(longitd, latitud), c(LON, LAT)))
  
```

```{r}
edgeEllpCripple2019 = Cripple_near2019 %>% 
  rowwise() %>% 
  mutate(distEllp = distVincentyEllipsoid(c(longitd, latitud), c(LON, LAT), a=6378137, b=6356752.3142, f=1/298.257223563))
```

```{r}
edgeCripple2019
edgeSphCripple2019
edgeEllpCripple2019
```

#### Combine into single DF
```{r}
joinCripple2019_1 = edgeCripple2019 %>%
  full_join(edgeSphCripple2019, by = c("project", "FireYr", "fir_scr", "offcl__", "site", "plot", "latitud", "longitd", "elevatn", "slope", "aspect", "mstr_cl" )) %>%
  full_join(edgeEllpCripple2019, by = c("project", "FireYr", "fir_scr", "offcl__", "site", "plot", "latitud", "longitd", "elevatn", "slope", "aspect", "mstr_cl", "LAT", "LON" )) %>%
  drop_units()

joinCripple2019_1
```

## 2019 Frozen Calf
### Data
```{r}
Frozen2019 = st_read("../data/PerimeterPoints/frozenPtsLatLon2019.shp", "frozenPtsLatLon2019")
```

### 2D Find nearest point and measure distance
```{r}
edgeFrozen2019=fieldFrozen2019 %>%
  mutate(nearestEdge = st_nearest_feature(., Frozen2019)) %>%
  mutate(edgeEa = st_distance(., Frozen2019[nearestEdge,], by_element=TRUE, which = "Euclidean")) %>%
  st_drop_geometry(.)

```


### 3D
#### join nearest feature
 Join df with df1, based on the nearest feature:
```{r}
Frozen_near2019 <- st_join(fieldFrozen2019, Frozen2019, join = st_nearest_feature) %>%
  st_drop_geometry(.) %>%
  dplyr::select(-offcl__.y, -FireYr.y) %>%
  rename(FireYr = FireYr.x, offcl__ = offcl__.x)
```

```{r}
Frozen_near2019
```
```{r}
edgeSphFrozen2019 = Frozen_near2019 %>% 
  rowwise() %>% 
  mutate(distSph = distHaversine(c(longitd, latitud), c(LON, LAT)))
  
```

```{r}
edgeEllpFrozen2019 = Frozen_near2019 %>% 
  rowwise() %>% 
  mutate(distEllp = distVincentyEllipsoid(c(longitd, latitud), c(LON, LAT), a=6378137, b=6356752.3142, f=1/298.257223563))
```

```{r}
edgeFrozen2019
edgeSphFrozen2019
edgeEllpFrozen2019
```

#### Combine into single DF
```{r}
joinFrozen2019_1 = edgeFrozen2019 %>%
  full_join(edgeSphFrozen2019, by = c("project", "FireYr", "fir_scr", "offcl__", "site", "plot", "latitud", "longitd", "elevatn", "slope", "aspect", "mstr_cl" )) %>%
  full_join(edgeEllpFrozen2019, by = c("project", "FireYr", "fir_scr", "offcl__", "site", "plot", "latitud", "longitd", "elevatn", "slope", "aspect", "mstr_cl", "LAT", "LON" )) %>%
  drop_units()

joinFrozen2019_1
```

## 2019 Hess Creek
### Data

```{r}
Hess2019 = st_read("../data/PerimeterPoints/HessPtsLatLon2019.shp", "HessPtsLatLon2019")
```

### 2D Find nearest point and measure distance
```{r}
edgeHess2019=fieldHess2019 %>%
  mutate(nearestEdge = st_nearest_feature(., Hess2019)) %>%
  mutate(edgeEa = st_distance(., Hess2019[nearestEdge,], by_element=TRUE, which = "Euclidean")) %>%
  st_drop_geometry(.)

```


### 3D
#### join nearest feature
 Join df with df1, based on the nearest feature:
```{r}
Hess_near2019 <- st_join(fieldHess2019, Hess2019, join = st_nearest_feature) %>%
  st_drop_geometry(.) %>%
  dplyr::select(-offcl__.y, -FireYr.y) %>%
  rename(FireYr = FireYr.x, offcl__ = offcl__.x)
```

```{r}
Hess_near2019
```
```{r}
edgeSphHess2019 = Hess_near2019 %>% 
  rowwise() %>% 
  mutate(distSph = distHaversine(c(longitd, latitud), c(LON, LAT)))
  
```

```{r}
edgeEllpHess2019 = Hess_near2019 %>% 
  rowwise() %>% 
  mutate(distEllp = distVincentyEllipsoid(c(longitd, latitud), c(LON, LAT), a=6378137, b=6356752.3142, f=1/298.257223563))
```

```{r}
edgeHess2019
edgeSphHess2019
edgeEllpHess2019
```

#### Combine into single DF
```{r}
joinHess2019_1 = edgeHess2019 %>%
  full_join(edgeSphHess2019, by = c("project", "FireYr", "fir_scr", "offcl__", "site", "plot", "latitud", "longitd", "elevatn", "slope", "aspect", "mstr_cl" )) %>%
  full_join(edgeEllpHess2019, by = c("project", "FireYr", "fir_scr", "offcl__", "site", "plot", "latitud", "longitd", "elevatn", "slope", "aspect", "mstr_cl", "LAT", "LON" )) %>%
  drop_units()

joinHess2019_1
```


## 2019 Marr
###Data
```{r}
Marr2019 = st_read("../data/PerimeterPoints/MarrPtsLatLon2019.shp", "MarrPtsLatLon2019")
```

### 2D Find nearest point and measure distance
```{r}
edgeMarr2019=fieldMarr2019 %>%
  mutate(nearestEdge = st_nearest_feature(., Marr2019)) %>%
  mutate(edgeEa = st_distance(., Marr2019[nearestEdge,], by_element=TRUE, which = "Euclidean")) %>%
  st_drop_geometry(.)

```


### 3D
#### join nearest feature
 Join df with df1, based on the nearest feature:
```{r}
Marr_near2019 <- st_join(fieldMarr2019, Marr2019, join = st_nearest_feature) %>%
  st_drop_geometry(.) %>%
  dplyr::select(-offcl__.y, -FireYr.y) %>%
  rename(FireYr = FireYr.x, offcl__ = offcl__.x)
```

```{r}
Marr_near2019
```
```{r}
edgeSphMarr2019 = Marr_near2019 %>% 
  rowwise() %>% 
  mutate(distSph = distHaversine(c(longitd, latitud), c(LON, LAT)))
  
```

```{r}
edgeEllpMarr2019 = Marr_near2019 %>% 
  rowwise() %>% 
  mutate(distEllp = distVincentyEllipsoid(c(longitd, latitud), c(LON, LAT), a=6378137, b=6356752.3142, f=1/298.257223563))
```

```{r}
edgeMarr2019
edgeSphMarr2019
edgeEllpMarr2019
```

#### Combine into single DF
```{r}
joinMarr2019_1 = edgeMarr2019 %>%
  full_join(edgeSphMarr2019, by = c("project", "FireYr", "fir_scr", "offcl__", "site", "plot", "latitud", "longitd", "elevatn", "slope", "aspect", "mstr_cl" )) %>%
  full_join(edgeEllpMarr2019, by = c("project", "FireYr", "fir_scr", "offcl__", "site", "plot", "latitud", "longitd", "elevatn", "slope", "aspect", "mstr_cl", "LAT", "LON" )) %>%
  drop_units()

joinMarr2019_1
```


## 2019 Preach
### Data
```{r}
Preach2019 = st_read("../data/PerimeterPoints/PreachPtsLatLon2019.shp", "PreachPtsLatLon2019")
```

### 2D Find nearest point and measure distance
```{r}
edgePreach2019=fieldPreach2019 %>%
  mutate(nearestEdge = st_nearest_feature(., Preach2019)) %>%
  mutate(edgeEa = st_distance(., Preach2019[nearestEdge,], by_element=TRUE, which = "Euclidean")) %>%
  st_drop_geometry(.)

```


### 3D
#### join nearest feature
 Join df with df1, based on the nearest feature:
```{r}
Preach_near2019 <- st_join(fieldPreach2019, Preach2019, join = st_nearest_feature) %>%
  st_drop_geometry(.) %>%
  dplyr::select(-offcl__.y, -FireYr.y) %>%
  rename(FireYr = FireYr.x, offcl__ = offcl__.x)
```

```{r}
Preach_near2019
```
```{r}
edgeSphPreach2019 = Preach_near2019 %>% 
  rowwise() %>% 
  mutate(distSph = distHaversine(c(longitd, latitud), c(LON, LAT)))
  
```

```{r}
edgeEllpPreach2019 = Preach_near2019 %>% 
  rowwise() %>% 
  mutate(distEllp = distVincentyEllipsoid(c(longitd, latitud), c(LON, LAT), a=6378137, b=6356752.3142, f=1/298.257223563))
```

```{r}
edgePreach2019
edgeSphPreach2019
edgeEllpPreach2019
```

#### Combine into single DF
```{r}
joinPreach2019_1 = edgePreach2019 %>%
  full_join(edgeSphPreach2019, by = c("project", "FireYr", "fir_scr", "offcl__", "site", "plot", "latitud", "longitd", "elevatn", "slope", "aspect", "mstr_cl" )) %>%
  full_join(edgeEllpPreach2019, by = c("project", "FireYr", "fir_scr", "offcl__", "site", "plot", "latitud", "longitd", "elevatn", "slope", "aspect", "mstr_cl", "LAT", "LON" )) %>%
  drop_units()

joinPreach2019_1
```

## 2019 Shovel
### Data

```{r}
Shovel2019 = st_read("../data/PerimeterPoints/ShovelPtsLatLon2019.shp", "ShovelPtsLatLon2019")
```

### 2D Find nearest point and measure distance
```{r}
edgeShovel2019=fieldShovel2019 %>%
  mutate(nearestEdge = st_nearest_feature(., Shovel2019)) %>%
  mutate(edgeEa = st_distance(., Shovel2019[nearestEdge,], by_element=TRUE, which = "Euclidean")) %>%
  st_drop_geometry(.)

```


### 3D
#### join nearest feature
 Join df with df1, based on the nearest feature:
```{r}
Shovel_near2019 <- st_join(fieldShovel2019, Shovel2019, join = st_nearest_feature) %>%
  st_drop_geometry(.) %>%
  dplyr::select(-offcl__.y, -FireYr.y) %>%
  rename(FireYr = FireYr.x, offcl__ = offcl__.x)
```

```{r}
Shovel_near2019
```
```{r}
edgeSphShovel2019 = Shovel_near2019 %>% 
  rowwise() %>% 
  mutate(distSph = distHaversine(c(longitd, latitud), c(LON, LAT)))
  
```

```{r}
edgeEllpShovel2019 = Shovel_near2019 %>% 
  rowwise() %>% 
  mutate(distEllp = distVincentyEllipsoid(c(longitd, latitud), c(LON, LAT), a=6378137, b=6356752.3142, f=1/298.257223563))
```

```{r}
edgeShovel2019
edgeSphShovel2019
edgeEllpShovel2019
```

#### Combine into single DF
```{r}
joinShovel2019_1 = edgeShovel2019 %>%
  full_join(edgeSphShovel2019, by = c("project", "FireYr", "fir_scr", "offcl__", "site", "plot", "latitud", "longitd", "elevatn", "slope", "aspect", "mstr_cl" )) %>%
  full_join(edgeEllpShovel2019, by = c("project", "FireYr", "fir_scr", "offcl__", "site", "plot", "latitud", "longitd", "elevatn", "slope", "aspect", "mstr_cl", "LAT", "LON" )) %>%
  drop_units()

joinShovel2019_1
```

## 2019 Tractor Trail 2
### Data
```{r}
Tractor2019 = st_read("../data/PerimeterPoints/TractorPtsLatLon2019.shp", "TractorPtsLatLon2019")
```

### 2D Find nearest point and measure distance
```{r}
edgeTractor2019=fieldTractor2019 %>%
  mutate(nearestEdge = st_nearest_feature(., Tractor2019)) %>%
  mutate(edgeEa = st_distance(., Tractor2019[nearestEdge,], by_element=TRUE, which = "Euclidean")) %>%
  st_drop_geometry(.)

```


### 3D
#### join nearest feature
 Join df with df1, based on the nearest feature:
```{r}
Tractor_near2019 <- st_join(fieldTractor2019, Tractor2019, join = st_nearest_feature) %>%
  st_drop_geometry(.) %>%
  dplyr::select(-offcl__.y, -FireYr.y) %>%
  rename(FireYr = FireYr.x, offcl__ = offcl__.x)
```

```{r}
Tractor_near2019
```
```{r}
edgeSphTractor2019 = Tractor_near2019 %>% 
  rowwise() %>% 
  mutate(distSph = distHaversine(c(longitd, latitud), c(LON, LAT)))
  
```

```{r}
edgeEllpTractor2019 = Tractor_near2019 %>% 
  rowwise() %>% 
  mutate(distEllp = distVincentyEllipsoid(c(longitd, latitud), c(LON, LAT), a=6378137, b=6356752.3142, f=1/298.257223563))
```

```{r}
edgeTractor2019
edgeSphTractor2019
edgeEllpTractor2019
```

#### Combine into single DF
```{r}
joinTractor2019_1 = edgeTractor2019 %>%
  full_join(edgeSphTractor2019, by = c("project", "FireYr", "fir_scr", "offcl__", "site", "plot", "latitud", "longitd", "elevatn", "slope", "aspect", "mstr_cl" )) %>%
  full_join(edgeEllpTractor2019, by = c("project", "FireYr", "fir_scr", "offcl__", "site", "plot", "latitud", "longitd", "elevatn", "slope", "aspect", "mstr_cl", "LAT", "LON" )) %>%
  drop_units()

joinTractor2019_1
```

## 2019 2019BC005
### Data
```{r}
BC0052019 = st_read("../data/PerimeterPoints/BC005PtsLatLon2019.shp", "BC005PtsLatLon2019")
```


### 2D Find nearest point and measure distance
```{r}
edgeBC0052019=fieldBC0052019 %>%
  mutate(nearestEdge = st_nearest_feature(., BC0052019)) %>%
  mutate(edgeEa = st_distance(., BC0052019[nearestEdge,], by_element=TRUE, which = "Euclidean")) %>%
  st_drop_geometry(.)

```


### 3D
#### join nearest feature
 Join df with df1, based on the nearest feature:
```{r}
BC005_near2019 <- st_join(fieldBC0052019, BC0052019, join = st_nearest_feature) %>%
  st_drop_geometry(.) %>%
  dplyr::select(-offcl__.y, -FireYr.y) %>%
  rename(FireYr = FireYr.x, offcl__ = offcl__.x)
```

```{r}
BC005_near2019
```
```{r}
edgeSphBC0052019 = BC005_near2019 %>% 
  rowwise() %>% 
  mutate(distSph = distHaversine(c(longitd, latitud), c(LON, LAT)))
  
```

```{r}
edgeEllpBC0052019 = BC005_near2019 %>% 
  rowwise() %>% 
  mutate(distEllp = distVincentyEllipsoid(c(longitd, latitud), c(LON, LAT), a=6378137, b=6356752.3142, f=1/298.257223563))
```

```{r}
edgeBC0052019
edgeSphBC0052019
edgeEllpBC0052019
```

#### Combine into single DF
```{r}
joinBC0052019_1 = edgeBC0052019 %>%
  full_join(edgeSphBC0052019, by = c("project", "FireYr", "fir_scr", "offcl__", "site", "plot", "latitud", "longitd", "elevatn", "slope", "aspect", "mstr_cl" )) %>%
  full_join(edgeEllpBC0052019, by = c("project", "FireYr", "fir_scr", "offcl__", "site", "plot", "latitud", "longitd", "elevatn", "slope", "aspect", "mstr_cl", "LAT", "LON" )) %>%
  drop_units()

joinBC0052019_1
```

## 2019 2019MA014
###Data
```{r}
MA0142019 = st_read("../data/PerimeterPoints/MA014PtsLatLon2019.shp", "MA014PtsLatLon2019")
```


### 2D Find nearest point and measure distance
```{r}
edgeMA0142019=fieldMA0142019 %>%
  mutate(nearestEdge = st_nearest_feature(., MA0142019)) %>%
  mutate(edgeEa = st_distance(., MA0142019[nearestEdge,], by_element=TRUE, which = "Euclidean")) %>%
  st_drop_geometry(.)

```


### 3D
#### join nearest feature
 Join df with df1, based on the nearest feature:
```{r}
MA014_near2019 <- st_join(fieldMA0142019, MA0142019, join = st_nearest_feature) %>%
  st_drop_geometry(.) %>%
  dplyr::select(-offcl__.y, -FireYr.y) %>%
  rename(FireYr = FireYr.x, offcl__ = offcl__.x)
```

```{r}
MA014_near2019
```
```{r}
edgeSphMA0142019 = MA014_near2019 %>% 
  rowwise() %>% 
  mutate(distSph = distHaversine(c(longitd, latitud), c(LON, LAT)))
  
```

```{r}
edgeEllpMA0142019 = MA014_near2019 %>% 
  rowwise() %>% 
  mutate(distEllp = distVincentyEllipsoid(c(longitd, latitud), c(LON, LAT), a=6378137, b=6356752.3142, f=1/298.257223563))
```

```{r}
edgeMA0142019
edgeSphMA0142019
edgeEllpMA0142019
```

#### Combine into single DF
```{r}
joinMA0142019_1 = edgeMA0142019 %>%
  full_join(edgeSphMA0142019, by = c("project", "FireYr", "fir_scr", "offcl__", "site", "plot", "latitud", "longitd", "elevatn", "slope", "aspect", "mstr_cl" )) %>%
  full_join(edgeEllpMA0142019, by = c("project", "FireYr", "fir_scr", "offcl__", "site", "plot", "latitud", "longitd", "elevatn", "slope", "aspect", "mstr_cl", "LAT", "LON" )) %>%
  drop_units()

joinMA0142019_1
```

## Combine 2019
```{r}
combo2019_1 = rbind(joinBear2019_1, joinCripple2019_1)
combo2019_2 = rbind(joinFrozen2019_1, joinHess2019_1)
combo2019_3 = rbind(joinMarr2019_1, joinPreach2019_1)
combo2019_4 = rbind(joinShovel2019_1, joinTractor2019_1)
combo2019_5 = rbind(joinBC0052019_1, joinMA0142019_1)

combo2019_1_2 = rbind(combo2019_1, combo2019_2)
combo2019_3_4 = rbind(combo2019_3, combo2019_4)
combo20191To4 = rbind(combo2019_1_2,combo2019_3_4)
combo2019All = rbind(combo20191To4, combo2019_5)
```

```{r}
combo2019All
```


# 2020
## 2020 Isom
### Data
```{r}
isom2020 = st_read("../data/PerimeterPoints/IsomPtsLatLon2020.shp", "IsomPtsLatLon2020")
```
```{r}
isom2020
```

### 2D Find nearest point and measure distance
```{r}
edge2020=fieldpts2020 %>%
  mutate(nearestEdge = st_nearest_feature(., isom2020)) %>%
  mutate(edgeEa = st_distance(., isom2020[nearestEdge,], by_element=TRUE, which = "Euclidean")) %>%
  st_drop_geometry(.)

```


### 3D
#### join nearest feature
 Join df with df1, based on the nearest feature:
```{r}
isom_near2020 <- st_join(fieldpts2020, isom2020, join = st_nearest_feature) %>%
  st_drop_geometry(.) %>%
  dplyr::select(-offcl__.y, -FireYr.y) %>%
  rename(FireYr = FireYr.x, offcl__ = offcl__.x)
```

```{r}
isom_near2020
```
```{r}
edgeSph2020 = isom_near2020 %>% 
  rowwise() %>% 
  mutate(distSph = distHaversine(c(longitd, latitud), c(LON, LAT)))
  
```

```{r}
edgeEllp2020 = isom_near2020 %>% 
  rowwise() %>% 
  mutate(distEllp = distVincentyEllipsoid(c(longitd, latitud), c(LON, LAT), a=6378137, b=6356752.3142, f=1/298.257223563))
```

```{r}
edge2020
edgeSph2020
edgeEllp2020
```
#### Combine into single DF
```{r}
join2020_1 = edge2020 %>%
  full_join(edgeSph2020, by = c("project", "FireYr", "fir_scr", "offcl__", "site", "plot", "latitud", "longitd", "elevatn", "slope", "aspect", "mstr_cl" )) %>%
  full_join(edgeEllp2020, by = c("project", "FireYr", "fir_scr", "offcl__", "site", "plot", "latitud", "longitd", "elevatn", "slope", "aspect", "mstr_cl", "LAT", "LON" )) %>%
  drop_units()

join2020_1
```

```{r}
join2020_1
```


## 2021 Munson Creek
### Data
```{r}
munson2021 = st_read("../data/PerimeterPoints/MunsonPtsLatLon2021.shp", "MunsonPtsLatLon2021")
```
```{r}
munson2021
```

### 2D Find nearest point and measure distance
```{r}
edge2021=fieldpts2021 %>%
  mutate(nearestEdge = st_nearest_feature(., munson2021)) %>%
  mutate(edgeEa = st_distance(., munson2021[nearestEdge,], by_element=TRUE, which = "Euclidean")) %>%
  st_drop_geometry(.)

```


### 3D
#### join nearest feature
 Join df with df1, based on the nearest feature:
```{r}
munson_near2021 <- st_join(fieldpts2021, munson2021, join = st_nearest_feature) %>%
  st_drop_geometry(.) %>%
  dplyr::select(-offcl__.y, -FireYr.y) %>%
  rename(FireYr = FireYr.x, offcl__ = offcl__.x)
```

```{r}
munson_near2021
```
```{r}
edgeSph2021 = munson_near2021 %>% 
  rowwise() %>% 
  mutate(distSph = distHaversine(c(longitd, latitud), c(LON, LAT)))
  
```

```{r}
edgeEllp2021 = munson_near2021 %>% 
  rowwise() %>% 
  mutate(distEllp = distVincentyEllipsoid(c(longitd, latitud), c(LON, LAT), a=6378137, b=6356752.3142, f=1/298.257223563))
```

```{r}
edge2021
edgeSph2021
edgeEllp2021
```
#### Combine into single DF
```{r}
join2021_1 = edge2021 %>%
  full_join(edgeSph2021, by = c("project", "FireYr", "fir_scr", "offcl__", "site", "plot", "latitud", "longitd", "elevatn", "slope", "aspect", "mstr_cl" )) %>%
  full_join(edgeEllp2021, by = c("project", "FireYr", "fir_scr", "offcl__", "site", "plot", "latitud", "longitd", "elevatn", "slope", "aspect", "mstr_cl", "LAT", "LON" )) %>%
  drop_units()

join2021_1
```

```{r}
join2021_1
```

# Stack rows for all fires & Years
```{r}
combo2015All
combo2019All
```

```{r}
join2020_1 
join2021_1
```

```{r}
comboYears1 = rbind(combo2015All, combo2019All)
comboYears2 = rbind(join2020_1, join2021_1)
ComboAllYears = rbind(comboYears1, comboYears2)

```

# Write to cvs
```{r}
write.csv(ComboAllYears,file = "../outputs/EdgeDistanceAll.csv")
```

