---
title: "Distance To Unburned Test"
author: "Anna Talucci"
date: '2022-10-20'
output: html_document
---
# Overview

Distance from field site to nearest unburned.

-- Process by fire year
-- Take Rasters
-- Convert raster to point 
--
-- Measure distance from point to polygon (st_distance or st_nearest maybe?)

# Packages

```{r}
library(tidyverse)
library(sp)
library(sf)
library(ids)
library(terra)
library(gdalUtilities)
library(geodist)
library(lwgeom)
library(geosphere)
```

# Projections
```{r}
wgs_proj = "+proj=longlat +datum=WGS84 +no_defs"
```

```{r}
ea_proj = "+proj=aea +lat_0=50 +lon_0=-154 +lat_1=55 +lat_2=65 +x_0=0 +y_0=0 +datum=NAD83 +units=m +no_defs"
```

# Data


## Field points by Year

```{r}
fieldpts2015 = st_read("../data/FieldPointsShp/FieldPoints2015.shp", "FieldPoints2015")
fieldpts2019 = st_read("../data/FieldPointsShp/FieldPoints2019.shp", "FieldPoints2019")
fieldpts2020 = st_read("../data/FieldPointsShp/FieldPoints2020.shp", "FieldPoints2020")
fieldpts2021 = st_read("../data/FieldPointsShp/FieldPoints2021.shp", "FieldPoints2021")
```

## Unburned points
```{r}
unburned2015 = st_read("../data/UnburnedPoints/UnburnedPtsLatLon2015.shp", "UnburnedPtsLatLon2015")
unburned2019 = st_read("../data/UnburnedPoints/UnburnedPtsLatLon2019.shp", "UnburnedPtsLatLon2019")
unburned2020 = st_read("../data/UnburnedPoints/UnburnedPtsLatLon2020.shp", "UnburnedPtsLatLon2020")
unburned2021 = st_read("../data/UnburnedPoints/UnburnedPtsLatLon2021.shp", "UnburnedPtsLatLon2021")
```

```{r}
head(unburned2015)
```


# 2D--Distance to nearest unburned point (cartesian measure)

## 2015
```{r}
dist2015= fieldpts2015 %>%
  mutate(nearest = st_nearest_feature(., unburned2015)) %>%
  mutate(distEa = st_distance(., unburned2015[nearest,], by_element=TRUE)) %>%
  st_drop_geometry(.) 
```

```{r}
head(dist2015)
```
### Write to cvs
```{r}
write.csv(dist2015,file = "../outputs/UnburnedDistance2015.csv")
```

## 2019 
```{r}
dist2019= fieldpts2019 %>%
  mutate(nearest = st_nearest_feature(., unburned2019)) %>%
  mutate(distEa = st_distance(., unburned2019[nearest,], by_element=TRUE)) %>%
  st_drop_geometry(.)
```

### Write to cvs
```{r}
write.csv(dist2019,file = "../outputs/UnburnedDistance2019.csv")
```

## 2020 
```{r}
dist2020= fieldpts2020 %>%
  mutate(nearest = st_nearest_feature(., unburned2020)) %>%
  mutate(distEa = st_distance(., unburned2020[nearest,], by_element=TRUE)) %>%
  st_drop_geometry(.)
```

### Write to cvs
```{r}
write.csv(dist2020,file = "../outputs/UnburnedDistance2020.csv")
```


## 2021 
```{r}
dist2021= fieldpts2021 %>%
  mutate(nearest = st_nearest_feature(., unburned2021)) %>%
  mutate(distEa = st_distance(., unburned2021[nearest,], by_element=TRUE, which = "Euclidean")) %>%
  st_drop_geometry(.)
```

```{r}
dist2021
```
### Write to cvs
```{r}
write.csv(dist2021,file = "../outputs/UnburnedDistance2021.csv")
```


# 3D--Distance to unburned (geodesic measure)

## 2015
### view dataframe
```{r}
fieldpts2015
unburned2015
```

### transform to wgs 84
```{r}
fieldpts2015wgs = st_transform(fieldpts2015, crs = wgs_proj)
unburned2015wgs = st_transform(unburned2015, crs = wgs_proj)
```

### join nearest feature
```{r}
# Join df with df1, based on the nearest feature:
df_near2015 <- st_join(fieldpts2015, unburned2015, join = st_nearest_feature) %>%
  st_drop_geometry(.) 
```

```{r}
df_near2015
```
### Calculate dist Spheroid
```{r}
dist_sph2015 = df_near2015 %>% 
  rowwise() %>% 
  mutate(distSph = distHaversine(c(longitd, latitud), c(LON, LAT)))
  
```

### Calculate distance Ellipsoid
```{r}
dist_ellp2015 = df_near2015 %>% 
  rowwise() %>% 
  mutate(distEllp = distVincentyEllipsoid(c(longitd, latitud), c(LON, LAT), a=6378137, b=6356752.3142, f=1/298.257223563))
```

## 2019
### view dataframe
```{r}
fieldpts2019
unburned2019
```

### transform to wgs 84
```{r}
fieldpts2019wgs = st_transform(fieldpts2019, crs = wgs_proj)
unburned2019wgs = st_transform(unburned2019, crs = wgs_proj)
```

### join nearest feature
```{r}
# Join df with df1, based on the nearest feature:
df_near2019 <- st_join(fieldpts2019, unburned2019, join = st_nearest_feature) %>%
  st_drop_geometry(.) 
```

```{r}
df_near2019
```
 
```{r}
dist_sph2019 = df_near2019 %>% 
  rowwise() %>% 
  mutate(distSph = distHaversine(c(longitd, latitud), c(LON, LAT)))
  
```

```{r}
dist_ellp2019 = df_near2019 %>% 
  rowwise() %>% 
  mutate(distEllp = distVincentyEllipsoid(c(longitd, latitud), c(LON, LAT), a=6378137, b=6356752.3142, f=1/298.257223563))
```

## 2020
### view dataframe
```{r}
fieldpts2020
unburned2020
```

### transform to wgs 84
```{r}
fieldpts2020wgs = st_transform(fieldpts2020, crs = wgs_proj)
unburned2020wgs = st_transform(unburned2020, crs = wgs_proj)
```

### join nearest feature
```{r}
# Join df with df1, based on the nearest feature:
df_near2020 <- st_join(fieldpts2020, unburned2020, join = st_nearest_feature) %>%
  st_drop_geometry(.) 
```

```{r}
df_near2020
```
 
```{r}
dist_sph2020 = df_near2020 %>% 
  rowwise() %>% 
  mutate(distSph = distHaversine(c(longitd, latitud), c(LON, LAT)))
  
```

```{r}
dist_ellp2020 = df_near2020 %>% 
  rowwise() %>% 
  mutate(distEllp = distVincentyEllipsoid(c(longitd, latitud), c(LON, LAT), a=6378137, b=6356752.3142, f=1/298.257223563))
```

## 2021

### view dataframe
```{r}
fieldpts2021
unburned2021
```

### transform to wgs 84
```{r}
fieldpts2021wgs = st_transform(fieldpts2021, crs = wgs_proj)
unburned2021wgs = st_transform(unburned2021, crs = wgs_proj)
```

### join nearest feature
```{r}
# Join df with df1, based on the nearest feature:
df_near2021 <- st_join(fieldpts2021, unburned2021, join = st_nearest_feature) %>%
  st_drop_geometry(.) 
```

```{r}
df_near2021
```
 
```{r}
dist_sph2021 = df_near2021 %>% 
  rowwise() %>% 
  mutate(distSph = distHaversine(c(longitd, latitud), c(LON, LAT)))
  
```

```{r}
dist_ellp2021 = df_near2021 %>% 
  rowwise() %>% 
  mutate(distEllp = distVincentyEllipsoid(c(longitd, latitud), c(LON, LAT), a=6378137, b=6356752.3142, f=1/298.257223563))
```


# Combine data into Single Dataframe
```{r}
dist2021
dist_sph2021
dist_ellp2021
```

```{r}
dist2019
dist_sph2019
dist_ellp2019
```

## Combine Colums for each year

### 2015

```{r}
join2015_1 = dist2015 %>%
  full_join(dist_sph2015, by = c("project", "FireYr", "fir_scr", "offcl__", "site", "plot", "latitud", "longitd", "elevatn", "slope", "aspect", "mstr_cl" )) %>%
  full_join(dist_ellp2015, by = c("project", "FireYr", "fir_scr", "offcl__", "site", "plot", "latitud", "longitd", "elevatn", "slope", "aspect", "mstr_cl", "UniqueId", "unburned", "LAT", "LON" )) %>%
  drop_units()

join2015_1
```

### 2019

```{r}
join2019_1 = dist2019 %>%
  full_join(dist_sph2019, by = c("project", "FireYr", "fir_scr", "offcl__", "site", "plot", "latitud", "longitd", "elevatn", "slope", "aspect", "mstr_cl" )) %>%
  full_join(dist_ellp2019, by = c("project", "FireYr", "fir_scr", "offcl__", "site", "plot", "latitud", "longitd", "elevatn", "slope", "aspect", "mstr_cl", "UniqueId", "unburned", "LAT", "LON" )) %>%
  drop_units()

join2019_1
```

### 2020

```{r}
join2020_1 = dist2020 %>%
  full_join(dist_sph2020, by = c("project", "FireYr", "fir_scr", "offcl__", "site", "plot", "latitud", "longitd", "elevatn", "slope", "aspect", "mstr_cl" )) %>%
  full_join(dist_ellp2020, by = c("project", "FireYr", "fir_scr", "offcl__", "site", "plot", "latitud", "longitd", "elevatn", "slope", "aspect", "mstr_cl", "UniqueId", "unburned", "LAT", "LON" )) %>%
  drop_units()

join2020_1
```

### 2021
```{r}
join2021_1 = dist2021 %>%
  full_join(dist_sph2021, by = c("project", "FireYr", "fir_scr", "offcl__", "site", "plot", "latitud", "longitd", "elevatn", "slope", "aspect", "mstr_cl" )) %>%
  full_join(dist_ellp2021, by = c("project", "FireYr", "fir_scr", "offcl__", "site", "plot", "latitud", "longitd", "elevatn", "slope", "aspect", "mstr_cl", "UniqueId", "unburned", "LAT", "LON" )) %>%
  drop_units()

join2021_1
```

## Stack rows to combine years
```{r}
combo1 = rbind(join2015_1, join2019_1)
combo2 = rbind(join2020_1, join2021_2)
combo3 = rbind(combo1, combo2)
```

```{r}
final = combo3 %>% dplyr::select(project:mstr_cl, distEa, distSph, distEllp)
```

```{r}
write.csv(final,file = "../outputs/DistUnburnedPixAll.csv")
```
**THE END**