---
title: "Distance to perimeter"
author: "Anna Talucci"
date: '2022-10-18'
output: html_document
---

# Overview

Distance from field site to perimeter.

-- Create spatial point file
-- Measure distance from point to polygon (st_distance or st_nearest maybe?)

# Packages

```{r}
library(tidyverse)
library(sp)
library(sf)
library(ids)
```

# Data

```{r}
field = read.csv("../data/field/FiSl_and_LegC_SiteData_FireYr.csv")
```

```{r}
head(field)
```
```{r}
fires = st_read("../data/firePolygons/AK_CA_firePolygons.shp", "AK_CA_firePolygons")
```

```{r}
fires
```
```{r}
head(fires)
tail(fires)
```
```{r}
plot(st_geometry(fires))
```
```{r}
fires %>% filter(FireYear == 2015 ) %>%
  ggplot() + 
  geom_sf() +
  coord_sf()
```
```{r}
fires %>% filter(FireYear == 2019 ) %>%
  ggplot() + 
  geom_sf() +
  coord_sf()
```
```{r}
fires %>% filter(FireYear == 2020 ) %>%
  ggplot() + 
  geom_sf() +
  coord_sf()
```

```{r}
fires %>% filter(FireYear == 2021 ) %>%
  ggplot() + 
  geom_sf() +
  coord_sf()
```
# Fire perimeter projection
```{r}
st_crs(fires)$proj4string
st_crs(fires)$epsg
```
# Projections
```{r}
wgs_proj = "+proj=longlat +datum=WGS84 +no_defs"
```

```{r}
ea_proj = "+proj=aea +lat_0=50 +lon_0=-154 +lat_1=55 +lat_2=65 +x_0=0 +y_0=0 +datum=NAD83 +units=m +no_defs"
```

```{r}
proj_aeqd = "+proj=aeqd +lat_0=90 +lon_0=0 +x_0=0 +y_0=0 +ellps=WGS84 +datum=WGS84 +units=m +no_defs" 
```

# Create spatial points
```{r}
coords_df = cbind(field$longitude, field$latitude)
df_pt <- SpatialPointsDataFrame(coords_df, proj4string = CRS(wgs_proj), data = field)
```

## Transform from sp to sf

```{r}
field_pt = st_as_sf(df_pt)
```
```{r}
head(field_pt)
```
## Plot points
```{r}
plot(st_geometry(field_pt))
```



# Transform to polar azimuthal equidistant projection
```{r}
fires_aeqd = st_transform(fires, crs = proj_aeqd)
field_aeqd = st_transform(field_pt, crs = proj_aeqd)
```


```{r}
plot(st_geometry(fires_aeqd))
plot(st_geometry(field_aeqd), add=T)
```

## Distance to nearest polygon
```{r}
test=field_aeqd %>%
  mutate(nearest = st_nearest_feature(.,fires_aeqd)) %>%
  mutate(dist_m = st_distance(., fires_aeqd[nearest,], by_element=TRUE)) %>%
  st_drop_geometry(.)
```

```{r}
min(test$dist_m)
max(test$dist_m)
mean(test$dist_m)
median(test$dist_m)
```
```{r}
test
```

# Transform to polar azimuthal equidistant projection
```{r}

field_albers = st_transform(field_pt, crs = st_crs(fires))
```


```{r}
plot(st_geometry(fires))
plot(st_geometry(field_albers), add=T)
```

## Distance to nearest polygon
```{r}
test2=field_albers %>%
  mutate(nearest = st_nearest_feature(.,fires)) %>%
  mutate(dist_m = st_distance(., fires[nearest,], by_element=TRUE)) %>%
  st_drop_geometry(.)
```

```{r}
min(test2$dist_m)
max(test2$dist_m)
mean(test2$dist_m)
median(test2$dist_m)
```