---
title: "PerimeterToPointsPlusLatLon"
author: "Anna Talucci"
date: '2022-11-07'
output: html_document
---

# Overview

Convert perimeter (polygon) to points add lat lon coords for each point

# Packages

```{r}
library(tidyverse)
library(sp)
library(sf)
library(ids)
library(units)
library(geosphere)
```

# Projections
```{r}
wgs_proj = "+proj=longlat +datum=WGS84 +no_defs"
```

```{r}
ea_proj = "+proj=aea +lat_0=50 +lon_0=-154 +lat_1=55 +lat_2=65 +x_0=0 +y_0=0 +datum=NAD83 +units=m +no_defs"
```



# Data
## Raster
```{r}
lat2015<-rast("../data/rasters/UnburnedLatLon/Lat2015.tif")
lon2015<-rast("../data/rasters/UnburnedLatLon/Lon2015.tif")
```

```{r}
lat2019<-rast("../data/rasters/UnburnedLatLon/Lat2019.tif")
lon2019<-rast("../data/rasters/UnburnedLatLon/Lon2019.tif")
```

```{r}
lat2020<-rast("../data/rasters/UnburnedLatLon/Lat2020.tif")
lon2020<-rast("../data/rasters/UnburnedLatLon/Lon2020.tif")
```

```{r}
lat2021<-rast("../data/rasters/UnburnedLatLon/Lat2021.tif")
lon2021<-rast("../data/rasters/UnburnedLatLon/Lon2021.tif")
```



# 2015 
## Aggie
### Data
```{r}
aggie2015 = st_read("../data/firePerimeters/AggieCreek2015AK/515_Aggie_Creek_20150721_0500.shp", "515_Aggie_Creek_20150721_0500")
```

### Transform to Equal area projection
```{r}
aggie2015ea = st_transform(aggie2015, crs = ea_proj)
```

### Convert to points

```{r}
fireaggie2015 = 
  st_geometry(obj = aggie2015ea) %>% 
  st_cast(to = 'MULTILINESTRING') %>% 
  st_cast(to = 'LINESTRING') %>% 
  st_cast(to = 'MULTIPOINT') %>% 
  st_cast(to = 'POINT') %>%
  st_as_sf(.) %>%
  st_zm(., drop = TRUE)
```

### Extract Lat/Lon

```{r}
aggielonValue2015=extract(lon2015, fireaggie2015)
aggielatValue2015=extract(lat2015, fireaggie2015)
```


### Combine & add fire name and year
```{r}
combineaggie2015=cbind(fireaggie2015, aggielatValue2015, aggielonValue2015)
aggieptLatLon2015 = combineaggie2015 %>% 
  mutate(FireYr = aggie2015$FIREYEAR) %>%
  mutate(offcl__ = aggie2015$NAME) %>%
  dplyr::select(offcl__, FireYr, LAT, LON, x)
```

### save 
```{r}
st_write(aggieptLatLon2015, "../outputs/PerimeterPoints/AggiePtsLatLon2015.shp", driver="ESRI Shapefile")
```

## Baker
### Data
```{r}
baker2015 = st_read("../data/firePerimeters/Baker2015AK/456_Baker_20150724_1630.shp", "456_Baker_20150724_1630")
```

### Transform to Equal area projection
```{r}
baker2015ea = st_transform(baker2015, crs = ea_proj)
```

### Convert to points

```{r}
firebaker2015 = 
  st_geometry(obj = baker2015ea) %>% 
  st_cast(to = 'MULTILINESTRING') %>% 
  st_cast(to = 'LINESTRING') %>% 
  st_cast(to = 'MULTIPOINT') %>% 
  st_cast(to = 'POINT') %>%
  st_as_sf(.) %>%
  st_zm(., drop = TRUE)
```

### Extract Lat/Lon

```{r}
bakerlonValue2015=extract(lon2015, firebaker2015)
bakerlatValue2015=extract(lat2015, firebaker2015)
```


### Combine & add fire name and year
```{r}
combinebaker2015=cbind(firebaker2015, bakerlatValue2015, bakerlonValue2015)
bakerptLatLon2015 = combinebaker2015 %>% 
  mutate(FireYr = baker2015$FIREYEAR) %>%
  mutate(offcl__ = baker2015$NAME) %>%
  dplyr::select(offcl__, FireYr, LAT, LON, x)
```

### save 
```{r}
st_write(bakerptLatLon2015, "../outputs/PerimeterPoints/BakerPtsLatLon2015.shp", driver="ESRI Shapefile")
```

## US Creek
### Data
```{r}
uscreek2015 = st_read("../data/firePerimeters/USCreek2015AK/531_U__S__Creek_20150804_1400.shp", "531_U__S__Creek_20150804_1400")
```

### Transform to Equal area projection
```{r}
uscreek2015ea = st_transform(uscreek2015, crs = ea_proj)
```

### Convert to points

```{r}
fireuscreek2015 = 
  st_geometry(obj = uscreek2015ea) %>% 
  st_cast(to = 'MULTILINESTRING') %>% 
  st_cast(to = 'LINESTRING') %>% 
  st_cast(to = 'MULTIPOINT') %>% 
  st_cast(to = 'POINT') %>%
  st_as_sf(.) %>%
  st_zm(., drop = TRUE)
```

### Extract Lat/Lon

```{r}
uscreeklonValue2015=extract(lon2015, fireuscreek2015)
uscreeklatValue2015=extract(lat2015, fireuscreek2015)
```


### Combine & add fire name and year
```{r}
combineuscreek2015=cbind(fireuscreek2015, uscreeklatValue2015, uscreeklonValue2015)
uscreekptLatLon2015 = combineuscreek2015 %>% 
  mutate(FireYr = uscreek2015$FIREYEAR) %>%
  mutate(offcl__ = uscreek2015$NAME) %>%
  dplyr::select(offcl__, FireYr, LAT, LON, x)
```

### save 
```{r}
st_write(uscreekptLatLon2015, "../outputs/PerimeterPoints/USCreekPtsLatLon2015.shp", driver="ESRI Shapefile")
```

# 2019
## Bear 
### Data

```{r}
bearnose2019 = st_read("../data/firePerimeters/BearnoseHill2019AK/407_Bearnose_Hill__20190905_1400.shp", "407_Bearnose_Hill__20190905_1400")
```
### Transform to Equal area projection
```{r}
bearnose2019ea = st_transform(bearnose2019, crs = ea_proj)
```

### Convert to points
```{r}
firebear2019 = 
  st_geometry(obj = bearnose2019ea) %>% 
  st_cast(to = 'MULTILINESTRING') %>% 
  st_cast(to = 'LINESTRING') %>% 
  st_cast(to = 'MULTIPOINT') %>% 
  st_cast(to = 'POINT') %>%
  st_as_sf(.) %>%
  st_zm(., drop = TRUE)
```

### Extract Lat/Lon
```{r}
bearlonValue2019=extract(lon2019, firebear2019)
bearlatValue2019=extract(lat2019, firebear2019)
```

### Combine & add fire name and year
```{r}
combineBear2019=cbind(firebear2019, bearlatValue2019, bearlonValue2019)
bearptLatLon2019 = combineBear2019 %>% 
  mutate(FireYr = bearnose2019$FIREYEAR) %>%
  mutate(offcl__ = bearnose2019$NAME) %>%
  dplyr::select(offcl__, FireYr, LAT, LON, x)
```

### save 
```{r}
st_write(bearptLatLon2019, "../outputs/PerimeterPoints/BearPtsLatLon2019.shp", driver="ESRI Shapefile")
```

## Cripple
### Data
```{r}
cripple2019 = st_read("../data/firePerimeters/CrippleCreek2019AK/201_Cripple_Creek_20190622_1337.shp", "201_Cripple_Creek_20190622_1337")
```
### Transform to Equal area projection
```{r}
cripple2019ea = st_transform(cripple2019, crs = ea_proj)
```

### Convert to points
```{r}
firecripple2019 = 
  st_geometry(obj = cripple2019ea) %>% 
  st_cast(to = 'MULTILINESTRING') %>% 
  st_cast(to = 'LINESTRING') %>% 
  st_cast(to = 'MULTIPOINT') %>% 
  st_cast(to = 'POINT') %>%
  st_as_sf(.) %>%
  st_zm(., drop = TRUE)
```

### Extract Lat/Lon
```{r}
cripplelonValue2019=extract(lon2019, firecripple2019)
cripplelatValue2019=extract(lat2019, firecripple2019)
```

### Combine & add fire name and year
```{r}
combinecripple2019=cbind(firecripple2019, cripplelatValue2019, cripplelonValue2019)
crippleptLatLon2019 = combinecripple2019 %>% 
  mutate(FireYr = cripple2019$FIREYEAR) %>%
  mutate(offcl__ = cripple2019$NAME) %>%
  dplyr::select(offcl__, FireYr, LAT, LON, x)
```

### save 
```{r}
st_write(crippleptLatLon2019, "../outputs/PerimeterPoints/CripplePtsLatLon2019.shp", driver="ESRI Shapefile")
```

## Frozen Calf
### Data
```{r}
frozen2019 = st_read("../data/firePerimeters/FrozenCalf2019AK/367_Frozen_Calf__20190909_1300.shp", "367_Frozen_Calf__20190909_1300")
```

### Transform to Equal area projection
```{r}
frozen2019ea = st_transform(frozen2019 , crs = ea_proj)
```

### Convert to points
```{r}
firefrozen2019 = 
  st_geometry(obj = frozen2019ea) %>% 
  st_cast(to = 'MULTILINESTRING') %>% 
  st_cast(to = 'LINESTRING') %>% 
  st_cast(to = 'MULTIPOINT') %>% 
  st_cast(to = 'POINT') %>%
  st_as_sf(.) %>%
  st_zm(., drop = TRUE)
```

### Extract Lat/Lon
```{r}
frozenlonValue2019=extract(lon2019, firefrozen2019)
frozenlatValue2019=extract(lat2019, firefrozen2019)
```

### Combine & add fire name and year
```{r}
combinefrozen2019=cbind(firefrozen2019, frozenlatValue2019, frozenlonValue2019)
frozenptLatLon2019 = combinefrozen2019 %>% 
  mutate(FireYr = frozen2019$FIREYEAR) %>%
  mutate(offcl__ = frozen2019$NAME) %>%
  dplyr::select(offcl__, FireYr, LAT, LON, x)
```

### save 
```{r}
st_write(frozenptLatLon2019, "../outputs/PerimeterPoints/frozenPtsLatLon2019.shp", driver="ESRI Shapefile")
```


## Hess Creak
### Data

```{r}
hess2019 = st_read("../data/firePerimeters/HessCreek2019AK/324_Hess_Creek_20190831_1400.shp", "324_Hess_Creek_20190831_1400")
```

### Transform to Equal area projection
```{r}
hess2019ea = st_transform(hess2019, crs = ea_proj)
```

### Convert to points
```{r}
firehess2019 = 
  st_geometry(obj = hess2019ea) %>% 
  st_cast(to = 'MULTILINESTRING') %>% 
  st_cast(to = 'LINESTRING') %>% 
  st_cast(to = 'MULTIPOINT') %>% 
  st_cast(to = 'POINT') %>%
  st_as_sf(.) %>%
  st_zm(., drop = TRUE)
```

### Extract Lat/Lon
```{r}
hesslonValue2019=extract(lon2019, firehess2019)
hesslatValue2019=extract(lat2019, firehess2019)
```

### Combine & add fire name and year
```{r}
combinehess2019=cbind(firehess2019, hesslatValue2019, hesslonValue2019)
hessptLatLon2019 = combinehess2019 %>% 
  mutate(FireYr = hess2019$FIREYEAR) %>%
  mutate(offcl__ = hess2019$NAME) %>%
  dplyr::select(offcl__, FireYr, LAT, LON, x)
```

### save 
```{r}
st_write(hessptLatLon2019, "../outputs/PerimeterPoints/HessPtsLatLon2019.shp", driver="ESRI Shapefile")
```

## Marr
###Data
```{r}
marr2019 = st_read("../data/firePerimeters/Marr2019AK/212_Marr_20190831_1400.shp", "212_Marr_20190831_1400")
```

### Transform to Equal area projection
```{r}
marr2019ea = st_transform(marr2019, crs = ea_proj)
```

### Convert to points
```{r}
firemarr2019 = 
  st_geometry(obj = marr2019ea) %>% 
  st_cast(to = 'MULTILINESTRING') %>% 
  st_cast(to = 'LINESTRING') %>% 
  st_cast(to = 'MULTIPOINT') %>% 
  st_cast(to = 'POINT') %>%
  st_as_sf(.) %>%
  st_zm(., drop = TRUE)
```

### Extract Lat/Lon
```{r}
marrlonValue2019=extract(lon2019, firemarr2019)
marrlatValue2019=extract(lat2019, firemarr2019)
```

### Combine & add fire name and year
```{r}
combinemarr2019=cbind(firemarr2019, marrlatValue2019, marrlonValue2019)
marrptLatLon2019 = combinemarr2019 %>% 
  mutate(FireYr = marr2019$FIREYEAR) %>%
  mutate(offcl__ = marr2019$NAME) %>%
  dplyr::select(offcl__, FireYr, LAT, LON, x)
```

### save 
```{r}
st_write(marrptLatLon2019, "../outputs/PerimeterPoints/MarrPtsLatLon2019.shp", driver="ESRI Shapefile")
```

## Preach
### Data
```{r}
preach2019 = st_read("../data/firePerimeters/PreacherCreek2019AK/567_Preacher_Creek_20190818_1400.shp", "567_Preacher_Creek_20190818_1400")
```

### Transform to Equal area projection
```{r}
preach2019ea = st_transform(preach2019, crs = ea_proj)
```

### Convert to points
```{r}
firepreach2019 = 
  st_geometry(obj = preach2019ea) %>% 
  st_cast(to = 'MULTILINESTRING') %>% 
  st_cast(to = 'LINESTRING') %>% 
  st_cast(to = 'MULTIPOINT') %>% 
  st_cast(to = 'POINT') %>%
  st_as_sf(.) %>%
  st_zm(., drop = TRUE)
```

### Extract Lat/Lon
```{r}
preachlonValue2019=extract(lon2019, firepreach2019)
preachlatValue2019=extract(lat2019, firepreach2019)
```

### Combine & add fire name and year
```{r}
combinepreach2019=cbind(firepreach2019, preachlatValue2019, preachlonValue2019)
preachptLatLon2019 = combinepreach2019 %>% 
  mutate(FireYr = preach2019$FIREYEAR) %>%
  mutate(offcl__ = preach2019$NAME) %>%
  dplyr::select(offcl__, FireYr, LAT, LON, x)
```

### save 
```{r}
st_write(preachptLatLon2019, "../outputs/PerimeterPoints/PreachPtsLatLon2019.shp", driver="ESRI Shapefile")
```


## Shovel
### Data

```{r}
shovel2019 = st_read("../data/firePerimeters/ShovelCreek2019AK/319_Shovel_Creek_20190730_1500.shp", "319_Shovel_Creek_20190730_1500")
```

### Transform to Equal area projection
```{r}
shovel2019ea = st_transform(shovel2019, crs = ea_proj)
```

### Convert to points
```{r}
fireshovel2019 = 
  st_geometry(obj = shovel2019ea) %>% 
  st_cast(to = 'MULTILINESTRING') %>% 
  st_cast(to = 'LINESTRING') %>% 
  st_cast(to = 'MULTIPOINT') %>% 
  st_cast(to = 'POINT') %>%
  st_as_sf(.) %>%
  st_zm(., drop = TRUE)
```

### Extract Lat/Lon
```{r}
shovellonValue2019=extract(lon2019, fireshovel2019)
shovellatValue2019=extract(lat2019, fireshovel2019)
```

### Combine & add fire name and year
```{r}
combineshovel2019=cbind(fireshovel2019, shovellatValue2019, shovellonValue2019)
shovelptLatLon2019 = combineshovel2019 %>% 
  mutate(FireYr = shovel2019$FIREYEAR) %>%
  mutate(offcl__ = shovel2019$NAME) %>%
  dplyr::select(offcl__, FireYr, LAT, LON, x)
```

### save 
```{r}
st_write(shovelptLatLon2019, "../outputs/PerimeterPoints/ShovelPtsLatLon2019.shp", driver="ESRI Shapefile")
```


## Tractor Trail 2
### Data
```{r}
tractor2019 = st_read("../data/firePerimeters/TractorTrail22019AK/348_Tractor_Trail_2_20190831_1400.shp", "348_Tractor_Trail_2_20190831_1400")
```

### Transform to Equal area projection
```{r}
tractor2019ea = st_transform(tractor2019, crs = ea_proj)
```

### Convert to points

```{r}
firetractor2019 = 
  st_geometry(obj = tractor2019ea) %>% 
  st_cast(to = 'MULTILINESTRING') %>% 
  st_cast(to = 'LINESTRING') %>% 
  st_cast(to = 'MULTIPOINT') %>% 
  st_cast(to = 'POINT') %>%
  st_as_sf(.) %>%
  st_zm(., drop = TRUE)
```

### Extract Lat/Lon

```{r}
tractorlonValue2019=extract(lon2019, firetractor2019)
tractorlatValue2019=extract(lat2019, firetractor2019)
```


### Combine & add fire name and year
```{r}
combinetractor2019=cbind(firetractor2019, tractorlatValue2019, tractorlonValue2019)
tractorptLatLon2019 = combinetractor2019 %>% 
  mutate(FireYr = tractor2019$FIREYEAR) %>%
  mutate(offcl__ = tractor2019$NAME) %>%
  dplyr::select(offcl__, FireYr, LAT, LON, x)
```

### save 
```{r}
st_write(tractorptLatLon2019, "../outputs/PerimeterPoints/TractorPtsLatLon2019.shp", driver="ESRI Shapefile")
```

# 2020
## Individual Fire perimeters
```{r}
isom2020 = st_read("../data/firePerimeters/Isom2020AK/187_Isom_Creek_20200705_1700.shp", "187_Isom_Creek_20200705_1700")
```


## Transform to Equal area projection
```{r}
isom2020ea = st_transform(isom2020, crs = ea_proj)
```

## Convert to points
```{r}
fireisom2020 = 
  st_geometry(obj = isom2020ea) %>% 
  st_cast(to = 'MULTILINESTRING') %>% 
  st_cast(to = 'LINESTRING') %>% 
  st_cast(to = 'MULTIPOINT') %>% 
  st_cast(to = 'POINT') %>%
  st_as_sf(.) %>%
  st_zm(., drop = TRUE)
```

## Extract Lat/Lon
```{r}
lonValue2020=extract(lon2020, fireisom2020)
latValue2020=extract(lat2020, fireisom2020)
```

## Combine & add fire name and year
```{r}
combinePointValue2020=cbind(fireisom2020, latValue2020, lonValue2020)
ptLatLon2020 = combinePointValue2020 %>% 
  mutate(FireYr = isom2020$FIREYEAR) %>%
  mutate(offcl__ = isom2020$NAME) %>%
  dplyr::select(offcl__, FireYr, LAT, LON, x)
```

```{r}
ptLatLon2020
```

## save 
```{r eval=FALSE, include=FALSE}
st_write(ptLatLon2020, "../outputs/PerimeterPoints/IsomPtsLatLon2020.shp", driver="ESRI Shapefile")
```

# 2021
## Individual Fire perimeters
```{r}
munson2021 = st_read("../data/firePerimeters/Munson2021AK/235_Munson_Creek_20210805_1337.shp", "235_Munson_Creek_20210805_1337")
```

## Transform to Equal area projection
```{r}
munson2021ea = st_transform(munson2021, crs = ea_proj)
```

## Check projection
```{r}
st_crs(munson2021ea)$proj4string
st_crs(munson2021ea)$epsg
```
## Check CRS
```{r}
crs(lat2021, proj=TRUE)
```

## Convert to points
```{r}
fireMunson2021 = 
  st_geometry(obj = fires2021ea) %>% 
  st_cast(to = 'MULTILINESTRING') %>% 
  st_cast(to = 'LINESTRING') %>% 
  st_cast(to = 'MULTIPOINT') %>% 
  st_cast(to = 'POINT') %>%
  st_as_sf(.) %>%
  st_zm(., drop = TRUE)
```

## Extract Lat/Lon
```{r}
lonValue2021=extract(lon2021, fireMunson2021)
latValue2021=extract(lat2021, fireMunson2021)
```

## Combine & add fire name and year
```{r}
combinePointValue2021=cbind(fireMunson2021, latValue2021, lonValue2021)
ptLatLon2021 = combinePointValue2021 %>% 
  mutate(FireYr = munson2021$FIREYEAR) %>%
  mutate(offcl__ = munson2021$NAME) %>%
  dplyr::select(offcl__, FireYr, LAT, LON, x)
```

```{r}
ptLatLon2021
```

## save 
```{r eval=FALSE, include=FALSE}
st_write(ptLatLon2021, "../outputs/PerimeterPoints/MunsonPtsLatLon2021.shp", driver="ESRI Shapefile")
```