---
title: "Unburned Raster to Points"
output: html_document
---

# Overview
Take unburned raster from GEE output, and convert to point shapefile. Processed in Equal area projection.

# Packages
```{r}
library(tidyverse)
library(sp)
library(sf)
library(ids)
library(terra)
library(gdalUtilities)
library(ids)
```
# Projections
```{r}
wgs_proj = "+proj=longlat +datum=WGS84 +no_defs"
```

```{r}
ea_proj = "+proj=aea +lat_0=50 +lon_0=-154 +lat_1=55 +lat_2=65 +x_0=0 +y_0=0 +datum=NAD83 +units=m +no_defs"
```

# Data

## Raster
```{r}
r2015<-rast("../data/rasters/unburnedMedian/unburned_Median2015.tif")
r2019<-rast("../data/rasters/unburnedMedian/unburned_Median2019.tif")
r2020<-rast("../data/rasters/unburnedMedian/unburned_Median2020.tif")
r2021<-rast("../data/rasters/unburnedMedian/unburned_Median2021.tif")
```

```{r eval=FALSE, include=FALSE}
r2015
r2019
r2020
r2021
```

```{r eval=FALSE, include=FALSE}
plot(r2015)
plot(r2019)
```


# Raster to points by year

## 2015 Raster to points
```{r}
r2015_pts = as.points(r2015, values=TRUE, na.rm=TRUE)
```

### Make into sf object
```{r}
pts2015 = st_as_sf(r2015_pts)
```

### Filter for unburned and add unique id
```{r}
set.seed(10)
unburned2015 = pts2015 %>% 
  filter(unburned==1) %>% 
  mutate(UniqueId = random_id(n= 205148, bytes = 4)) %>%
  dplyr::select(UniqueId, unburned, geometry)
```

```{r}
unburned2015
```


### Write to shapefile all points

```{r eval=FALSE, include=FALSE}
st_write(unburned2015, "../outputs/UnburnedPoints/UnburnedPoints2015.shp", driver="ESRI Shapefile")
```


## 2019 Raster to points
```{r}
r2019_pts = as.points(r2019, values=TRUE, na.rm=TRUE)
```

### Make into sf object
```{r}
pts2019 = st_as_sf(r2019_pts)
```

### Filter for unburned
```{r}
unburned2019 = pts2019  %>% 
  filter(unburned==1)
```

%>% 
  mutate(UniqueId = random_id(n= 205148, bytes = 4)) %>%
  dplyr::select(UniqueId, unburned, geometry)
### Write to shapefile all points

```{r eval=FALSE, include=FALSE}
st_write(unburned2019, "../outputs/UnburnedPoints/UnburnedPoints2019.shp", driver="ESRI Shapefile")
```

## 2020 Raster to points
```{r}
r2020_pts = as.points(r2020, values=TRUE, na.rm=TRUE)
```

### Make into sf object
```{r}
pts2020 = st_as_sf(r2020_pts)
```

### Filter for unburned
```{r}
unburned2020 = pts2020  %>% 
  filter(unburned==1) %>% 
  mutate(UniqueId = random_id(n= 2310, bytes = 4)) %>%
  dplyr::select(UniqueId, unburned, geometry)
```

```{r}
unburned2020
```
### Write to shapefile all points

```{r eval=FALSE, include=FALSE}
st_write(unburned2020, "../outputs/UnburnedPoints/UnburnedPoints2020.shp", driver="ESRI Shapefile")
```

## 2021 Raster to points
```{r}
r2021_pts = as.points(r2021, values=TRUE, na.rm=TRUE)
```

### Make into sf object
```{r}
pts2021 = st_as_sf(r2021_pts)
```

### Filter for unburned
```{r}
unburned2021 = pts2021  %>% 
  filter(unburned==1)%>% 
  mutate(UniqueId = random_id(n= 33486, bytes = 4)) %>%
  dplyr::select(UniqueId, unburned, geometry)
```

```{r}
unburned2021
```
### Write to shapefile all points

```{r eval=FALSE, include=FALSE}
st_write(unburned2021, "../outputs/UnburnedPoints/UnburnedPoints2021.shp", driver="ESRI Shapefile")
```